WORKING TITLE: The adaptive value of green nest material across birds: A systematic review and meta-analysis

### 2025-02-26 docs/supplementary_appendix.qmd
Search and selection section done

Prisma Eco-Evo Checklist @odea2021
:::

::: {#figsupp-string}
The search was conducted twice, the first time on 07.09.2022 and then repeated on 12.08.2024 to ensure it was the most up to date and did not miss any additional articles on the topic that were published meanwhile. For both the searches, we did not use any time limitation i.e. it included all the published literature till that given date. We used **Advance Search** option for both Web of Science Core Collection Database and Scopus Database using the search query given below.
:::

>>>>

Prisma Eco-Evo Checklist according to @odea2021
:::

::: {#figsupp-string}
The search was conducted twice, the first time on 07.09.2022 and then repeated on 12.08.2024 to ensure it was the most up to date and did not miss any additional articles on the topic that were published meanwhile. For both the searches, we did not use any time limitation i.e. it included all the published literature till that given date. We used **Advance Search** option for both Web of Science Core Collection Database and Scopus Database using the search query given below.\
\
Search string for the Web of Science Core Collection\
Databases used in the search included\
-Science Citation Index Expanded (SCI-EXPANDED) \[1900-present\]\
-Social Sciences Citation Index (SSCI) \[1900-present\]\
-Arts & Humanities Citation Index (AHCI) \[1975 - present\]\
-Conference Proceedings Citation Index - Science (CPCI-S) \[1991 - present\]\
-Conference Proceedings Citation Index - Social Science & Humanities (CPCI-SSH) \[1991 - present\]\
-Emerging Sources Citation Index (ESCI) \[2017- present\]\
\
We used advance search option and Title (TI), Abstract (AB) and Author Keywords (AK) to conduct our systematic search using the following string\
\

### 2025-02-26 manuscript_GNM.qmd
Search and selection section done

### Literature search

@@

unique_reference_list <- read_csv("data/unique_reference_list.csv")
full_reference_before_deduplication<-read_csv("data/full_reference_before_deduplication.csv")
selected_abstract_screening<-read_csv("data/selected_abstract_screening.csv")
```

We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022 and updated it on 12.08.2024. The search query was designed in three blocks to included terms for predictor/treatment (“green\*” OR “herb\*” OR “aromatic\*”) AND “nest\*”), population of interest (“bird\*” OR “aves” OR “avian” OR “ornithol\*” OR “passerine\*” OR “passeriform\*” OR “songbird\*” OR list of all bird genera) and only experimental studies ("experiment\*" OR "manipulat\*") (for complete search string tailored for specific database see @figsupp-string). We searched the title, abstract and keywords in English-language only with no restrictions on publication date or study type. We found `{r} nrow(unique_reference_list)` unique articles after removing `{r} nrow(full_reference_before_deduplication)-nrow(unique_reference_list)` duplicates using R package 'revtools' v0.4.1 (@westgate2019). We validated our search using an initial library of 15 key articles (\@figsupp-own-library), ensuring all were retrieved. Additionally, we used R package 'litsearchr' v1.0.0 (@grames2019) to confirm our keyword selection, which did not yield any new relevant terms.

All title and abstract screening were screened independently by atleast two screeners (SD,TR,JMGS) following a pre-designed decision tree (@figsupp-decision-tree) in revtools. We included all studies on birds that experimentally manipulated the green nest material (including aromatics or herbs) and measured any form of fitness proxy that can be used to address any of our hypothesis. `{r} nrow(selected_abstract_screening)` articles passed title and abstract screening.

Eligibility criteria

#### Study selection and eligibility criteria

-   Keyword search: where and when..

-   Justification for development of keyword search

-   Findings/Results of search

-   Exclusion criteria

@@

-   PRISMA Diagram link

>>>>

### Study selection and eligibility criteria

@@

unique_reference_list <- read_csv("data/unique_reference_list.csv")
full_reference_before_deduplication<-read_csv("data/full_reference_before_deduplication.csv")
selected_abstract_screening<-read_csv("data/selected_abstract_screening.csv")

# For updated search
unique_reference_list_repeat <- read_csv("data/unique_reference_repeat_12082024.csv")
full_reference_before_deduplication_repeat<-read_csv("data/full_reference_repeat_12082024.csv")
selected_abstract_screening_repeat<-read_csv("data/selected_abstract_screening_repeat.csv")

# For fulltext screening
excluded_fulltext <- read_csv("data/excluded_fulltext.csv")
```

We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022. The search query was designed in three blocks to included terms for predictor/treatment ("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*"), population of interest ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR list of all bird genera) and only experimental studies ("experiment\*" OR "manipulat\*") (for complete search string tailored to specific database see @figsupp-string). We searched the title, abstract and keywords in English-language only with no restrictions on publication date or study type. We found `{r} nrow(unique_reference_list)` unique articles after removing `{r} nrow(full_reference_before_deduplication)-nrow(unique_reference_list)` duplicates using R package 'revtools' v0.4.1 (@westgate2019). We validated our search using an initial library of 15 key articles (\@figsupp-own-library), ensuring all were retrieved. Additionally, we used R package 'litsearchr' v1.0.0 (@grames2019) to confirm our keyword selection, which did not yield any new relevant terms.

All title and abstract screening were screened independently by atleast two screeners (\~66% each by SD, TR, JMGS) following a pre-designed decision tree (@figsupp-decision-tree) in revtools. We included all studies on birds that experimentally manipulated the green nest material (including aromatics or herbs). `{r} nrow(selected_abstract_screening)` articles passed title and abstract screening and further evaluated in a fulltext screening by a single screener (\~33% each by SD, TR, JMGS) and double checked by another. We used the same criteria as above with an additional evaluation of whether the variable of interest in the article was a fitness proxy. `{r} nrow(excluded_fulltext)` articles were excluded and all conflicts in screening decision (\~1% for title and abstract screening and none for fulltext screening) were resolved through discussion.

We repeated our search using the same search string on 12.08.2024 and found `{r} nrow(full_reference_before_deduplication_repeat)` additional articles. After deduplicating, SD screened the title and abstract for the `{r} nrow(unique_reference_list_repeat)` unique articles using the same decision tree. We found `{r} sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T)` article by updating our search. In addition, we identified `{r}  nrow(selected_abstract_screening_repeat)-(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T))` articles through other sources that were not a part of our search. These studies met our inclusion criteria and were added to our meta-analysis. The exact number of screened and included studies along with reason of exclusion are shown in @figsupp-prisma-flowchart. We finally extracted data for `{r}  nrow(selected_abstract_screening_repeat) + (nrow(selected_abstract_screening)-nrow(excluded_fulltext))` articles and 2 unpublished studies. These were identified through our efforts to contact the authors of all included studies, and one dataset was provided by a co-author of this paper. <!--# Fix the code for generating this number later by using the data file directly to calculate the number of article -->

@@

<!-- -->
